Additional analyses

### 2023-11-01 procesamiento/prod_analysis-tables-macro.Rmd
update

@@

```{r oecd-clmm-macro,results='asis'}

@@

htmlreg(
  c(ocde_num_full_mac,ocde_num_strong_mac,ocde_num_weak_mac),
  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
  caption.above = T,
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

>>>>

```{r full-lmer-egalitarian-macro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())
coef_map <-
  list(
    homclass = "Homogeneity",
    logrgdpna = "log GDP",
    "gini_disp" = "GiniD ",
    "homclass:gini_disp" = "Hom:Gini(D)",
    "gini_mkt" = "Gini(M) ",
    "homclass:gini_mkt" = "Hom:Gini(M)",
    palmaratio               = "Palma",
    "homclass:palmawd"      = "Hom:Palma",
    top10             = "Top 10%",
    "homclass:top10"    = "Hom:top10",
    middle50             = "Bott.50%",
    "homclass:middle50"    = "Hom:bott50",
    d10d1             = "D10/D01",
    "homclass:d10d1"    = "Hom:D10D01",
    giniindex             = "Gini(WIID)",
    "homclass:giniindex"    = "Hom:Gini(WD)",
    ttheilge1             = "Theil",
    "homclass:ttheilge1"    = "Hom:Theil"
  )

@@

@@

knitreg(
  c(ocde_num_full_mac,ocde_num_strong_mac,ocde_num_weak_mac),
  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
  caption.above = T,
  stars = c(.001, .01, .05, .1),
  symbol = '\\dagger',
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```
